---
title: "Virtual Botanist"
author: "Zoran Ivankovich"
date: "12/1/2018"
output: pdf_document
latex_dependency: amsmath
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
setwd("~/Dropbox/cstats/virtual-botanist")
```

## 1 Problem 10.1 (a) and (b) - Fit a normal kernel density estimate for X

## a) Use bandwith derived the Sheather-Jones approach, Terrell's maximal smoothing principle.  Also plot the resulting density estimate along with the histogram of the data.  For Sheather-Jones method bandwith use Silverman's Rule of thumb as pilot h0 and the Normal kernel for L to estimate f''.  Then plug in to Equation 10.24 to get h for the final estimate of f.

Equation 10.24
$$
  h = \bigg(
    \frac
    {R(K)}
    {n\sigma_{K}^4R(f'')}
  \bigg)^{\frac{1}{5}} \text{ //}\sigma_K^2\text{ is the variance of K viewing K as density}
$$
```{r}
data2 <- read.csv(file = 'data2.csv', header = T, sep = ',')

leaves <- data2[, c('leaf', 'numEdges', 'area', 'perimeter', 'aspectRatio', 'rectangularity', 'circularity', 'equiDiameter', 'redMean', 'greenMean', 'blueMean', 'redVar', 'greenVar', 'blueVar')]
write.csv(leaves, file = "leaves.csv")
```

